### 2020-11-03 doc/manuscript/Dow_manuscript.Rmd
updated figure names/legends in manuscript

pheno_Tsensitivity_caption <- "Figure 4. Relationship between DOY and climwin mean tempeatures. For each 
observed climwin mean temperature value, the posterior mean of the fitted day of year
is represented by the solid blue line and credible intervals are represented by bands."

@@

```{r pheno_Tsensitivity, out.width="100%", echo=FALSE, fig.align="center", fig.cap=pheno_Tsensitivity_caption}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity.png")
```

@@

```{r DOYtiming2, out.width="100%", echo=FALSE, fig.align="center", fig.cap= DOYtiming_caption}
knitr::include_graphics("tables_figures/DOYtiming_HF_PRELIM.png")
```

>>>>

pheno_Tsensitivity_caption <- "Figure 4. Relationship between DOY and climwin mean temperatures. For each 
observed climwin mean temperature value, the posterior mean of the fitted day of year
is represented by the solid blue line and credible intervals are represented by bands."

@@

```{r pheno_Tsensitivity, out.width="100%", echo=FALSE, fig.align="center", fig.cap=pheno_Tsensitivity_caption}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity_scbi.png")
```

```{r , out.width="100%", echo=FALSE, fig.align="center", fig.cap="Harvard. FIGURES WILL NEED TO BE COMBINED"}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/pheno_Tsensitivity_HF.png")
```

@@
